Flowchart of Current Algorithm

### 2008-10-13 docs/flowchart/paper.tex
fixed the density advance section so it more accurately describes what the code does

  \item Compute the species edge states, $(\rho X_k)^{(1),\nph,\star}$,
  for the conservative update of $(\rho X_k)$. 
  Here we predict $\rho'$ and $X_k$ to the edges, using a second-order
  Taylor expansion in space and time, as described in paper II,
  Appendix A, using $\V = \uadvone+w_0^{\nph,\star} \er$.  We use the
  base state density, $\rho_0$, to convert these to edge states for
  $(\rho X_k)$.  We define $\rho^{(1),\nph,\star} = \sum_k (\rho
  X_k)^{(1),\nph,\star}.$

  \item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2),\star}$
  without explicitly including the reaction terms,
\begin{eqnarray}
(\rho X_k)^{(2),\star} &=& (\rho X_k)^{(1)} 
 - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho X_k)^{(1),\nph,\star} \right) \right] \enskip , \nonumber \\ \\
\rho^{(2),\star} &=& \sum_k (\rho X_k)^{(2),\star} \enskip , \\ 
X_k^{(2),\star} &=& (\rho X_k)^{(2),\star} / \rho^{(2),\star}
\end{eqnarray}

@@

\begin{eqnarray}
 \etarho^{\nph,\star}   &=&  {\rm {\bf Avg}} \left( (\uadvone \cdotb \er + w_0^{\nph,\star}) 
\rho^{(1),\nph,\star} \right) - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} 
 \enskip , \nonumber \\ \\
(\nabla\cdot\etarho\er)_j^{\nph,\star} &=& 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip , \\
 \psi_j^{\nph,\star}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{eqnarray}

@@

  \item Compute the species edge states, $(\rho X_k)^{(1),\nph}$, for
    the conservative update of $(\rho X_k)$. Here we predict $\rho'$
    and $X_k$ to the edges, using a second-order Taylor expansion in
    space and time, as described in paper II, Appendix A, using $\V =
    \uadvtwo+w_0^{\nph} \er$.  We use the base state density,
    $\rho_0$, to convert these to edge states for $(\rho X_k)$ and
    $(\rho h)$.  We define $\rho^{(1),\nph} = \sum_k (\rho
    X_k)^{(1),\nph}$.

    \item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2)}$
      without explicitly including the reaction terms,
\begin{eqnarray}
(\rho X_k)^{(2)} &=& (\rho X_k)^{(1)} 
- \dt \; \left[ \nablab \cdotb \left( (\uadvtwo+w_0^{\nph} \er)  
(\rho X_k)^{(1),\nph} \right) \right]  \enskip , \\ \nonumber \\
\rho^{(2)} &=& \sum_k (\rho X_k)^{(2)} \enskip , \\
X_k^{(2)} &=& (\rho X_k)^{(2)} / \rho^{(2)}
\end{eqnarray}

@@

\begin{eqnarray}
 \etarho^{\nph}   &=&  {\rm {\bf Avg}} \left( (\uadvtwo \cdotb \er + w_0^{\nph}) 
\rho^{(1),\nph} \right) - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip , \nonumber \\ \\
(\nabla\cdot\etarho\er)_j^{\nph} &=& 
\frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
 \psi_j^{\nph}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{eqnarray}

>>>>

  \item Compute the species edge states, $(\rho X_k)^{(1),\nph,\star}$,
  for the conservative update of $(\rho X_k)$. 
  Here we predict $\rho'$ and $X_k$ to the edges to obtain 
  $\rho^{'(1),\nph,\star}$ and $X_k^{(1),\nph,\star}$ using a second-order
  Taylor expansion in space and time, as described in paper II,
  Appendix A, using $\V = \uadvone+w_0^{\nph,\star} \er$.

  \item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2),\star}$
  without explicitly including the reaction terms,
\begin{eqnarray}
\rho^{(1),\nph,\star} &=& 
\left[\rho^{'(1),\nph,\star} + \left(\frac{\rho_0^n + \rho_0^{(2),\star}}{2}\right)\right] 
\enskip , \\
(\rho X_k)^{(2),\star} &=& (\rho X_k)^{(1)} 
 - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho X_k)^{(1),\nph,\star} \right) \right] \enskip , \nonumber \\ \\
\rho^{(2),\star} &=& \sum_k (\rho X_k)^{(2),\star} \enskip , \\ 
X_k^{(2),\star} &=& (\rho X_k)^{(2),\star} / \rho^{(2),\star}
\end{eqnarray}

@@

\begin{equation}
 \etarho^{\nph,\star} =  {\rm {\bf Avg}} \sum_k \left[ (\uadvone \cdotb \er + w_0^{\nph,\star}) (\rho X_k)^{(1),\nph,\star} \right] - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph,\star} = 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip ,
\end{equation}
\begin{equation}
 \psi_j^{\nph,\star} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{equation}

@@

  \item Compute the species edge states, $(\rho X_k)^{(1),\nph}$, for
    the conservative update of $(\rho X_k)$.  Here we predict $\rho'$ 
    and $X_k$ to the edges to obtain $\rho^{'(1),\nph}$ and 
    $X_k^{(1),\nph}$ using a second-order Taylor expansion in
    space and time, as described in paper II, Appendix A, using $\V =
    \uadvtwo+w_0^{\nph} \er$.

    \item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2)}$
      without explicitly including the reaction terms,
\begin{eqnarray}
\rho^{(1),\nph} &=& 
\left[\rho^{'(1),\nph} + \left(\frac{\rho_0^n + \rho_0^{(2)}}{2}\right)\right] 
\enskip , \\
(\rho X_k)^{(2)} &=& (\rho X_k)^{(1)} 
- \dt \; \left[ \nablab \cdotb \left( (\uadvtwo+w_0^{\nph} \er)  
(\rho X_k)^{(1),\nph} \right) \right]  \enskip , \\ \nonumber \\
\rho^{(2)} &=& \sum_k (\rho X_k)^{(2)} \enskip , \\
X_k^{(2)} &=& (\rho X_k)^{(2)} / \rho^{(2)}
\end{eqnarray}

@@

\begin{equation}
 \etarho^{\nph} = {\rm {\bf Avg}} \sum_k \left [\uadvtwo \cdotb \er + w_0^{\nph}) (\rho X_k)^{(1),\nph} \right] - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph} = \frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
\end{equation}
\begin{equation}
 \psi_j^{\nph} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{equation}
